```{r, warning = FALSE, message = FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(forcats)
library(ggthemes)
library(patchwork)
library(colorBlindness)
library ("purrr")
library(readr)
```

# Link to source
https://luisdva.github.io/rstats/model-cluster-plots/

```{r}
admixture_format <- function(k=2, path_wo_ext, path_pop=""){
    indiv <- read.table(paste(path_wo_ext,"fam", sep="."))["V2"]
    colnames(indiv) <- c("indiv")
    indiv$ID <- seq.int(nrow(indiv))
    
    if (path_pop!=""){
        pop <- read.table(path_pop,sep=",", col.name=c("species","indiv"))
        indiv <- left_join(indiv, pop)
    }

    q <-read.table(paste(path_wo_ext, k, "Q", sep="."),stringsAsFactors=T)
    q$ID <- seq.int(nrow(q))

    df <- merge(x=indiv, y=q, by="ID")

    if (path_pop == "") start <- 3
    else start <- 4
    end <- k+start-1
    
    data <- gather(df, key="popGroup", value="prob", start:end)
    return(data)
}
```


```{r}
admixture_plot <- function(data){
    k <- max(parse_number(data$popGroup))
    plot <-
    ggplot(data, aes(factor(indiv), prob, fill = factor(popGroup))) +
    geom_col(color = "gray", linewidth = 0.1) +
    theme_minimal() + labs(x = "", title = paste("K=",k,sep=""), y = "Admixture proportions") +
    scale_y_continuous(expand = c(0, 0)) +
    scale_x_discrete(expand = expansion(add = 1)) +
    theme(
        panel.spacing.x = unit(0.1, "lines"),
        axis.text.x = element_text(angle=90),
        strip.placement = "outside",
        legend.position = "none"
    ) +
    scale_fill_manual(values=Blue2Gray8Steps)

    if (!is_empty(data$species)) {
        plot <- plot+facet_grid(~fct_inorder(data$species), switch = "x", scales = "free", space = "free")
    }
    plot
}
```

# How to run it
`path_wo_ext` is a path to the header of admixture files (*.fam, *.Q) without extensions

`path_pop` is a path to the file with assignment groups for individuals (ex. population).

1st column there is the name of group.

2nd column is the name/code/ID of individual. The same as was used in *.fam

Parameter is optional. If you do not want to divide your data into facets, then omit.

```{r, out.width="100%", warning = FALSE, message = FALSE}
data <- admixture_format(k=3, path_wo_ext="/home/aliya/1BIOINF/1SEALIONS/admixture/Ejub_Q20_min80/NoLow_Ejub_snps_Q20_min80",
            path_pop="/home/aliya/1BIOINF/1SEALIONS/admixture/pop_indiv.csv")

admixture_plot(data)
```

```{r, out.width="100%", warning = FALSE, message = FALSE}
data <- admixture_format(k=3, path_wo_ext="/home/aliya/1BIOINF/1SEALIONS/admixture/all_Q20/Snps_Q20_NoMO40_noX",
            path_pop="/home/aliya/1BIOINF/1SEALIONS/admixture/pop_indiv.csv")

admixture_plot(data)
```
